Title Goes Here

### 2020-04-28 analysis/paper/paper.Rmd
add more description

@@

CV for each site
```{r}
cv_SYG6 + cv_SYG1_1 + cv_SYG1_2 +  plot_layout(ncol=1)
```

I'm working on how to read oulines and how to use them for anlaysis. We may not use this for the research.

```{r}
# reading landmarks and outline in tps, code from Morpho package, adjust readallTPS function. 
readalltps = function(file) 
{
    out = list()
    exOut <- FALSE
    noutline <- 0
    input <- readLines(file)
    LM <- grep("LM=", input)
    LMstring <- input[LM]
    nLM <- sapply(LMstring, strsplit, split = "=")
    nLM <- unlist(nLM)
    nLM <- as.integer(nLM[-which(nLM == "LM")])
    nobs <- length(nLM)
    ID <- grep("ID=", input)
    IDstring <- input[ID]
    nID <- sapply(IDstring, function(x) {
        x <- gsub("=", "_", x)
    })
    nID <- gsub(" ", "", unlist(nID))
    out$ID <- nID
    outline <- grep("CURVES=", input)
    if (length(outline) > 0) {
        exOut <- TRUE
        outlinestring <- input[outline]
        noutline <- sapply(outlinestring, strsplit, split = "=")
        noutline <- unlist(noutline)
        noutline <- as.integer(noutline[-which(noutline == "CURVES")])
        LMoutline <- (sapply(outline, function(x) {
            x <- max(which(LM < x))
        }))
    }
    LMdata <- list()
    for (i in 1:nobs) {
        if (nLM[i] > 0) {
            LMdata[[i]] <- as.numeric(unlist(strsplit(unlist(input[c((LM[i] + 
                1):(LM[i] + nLM[i]))]), split = " ")))
            LMdata[[i]] <- matrix(LMdata[[i]], nLM[i], 2, byrow = TRUE)
        }
        else LMdata[[i]] <- NA
    }
    names(LMdata) <- nID
    out$LM <- LMdata
    if (exOut) {
        outlineData <- list()
        for (i in 1:nobs) {
            if (i %in% LMoutline) {
                i1 <- grep(i, LMoutline)
                outlinetmp <- list()
                ptr <- outline[i1] + 1
                j <- 1
                while (j <= noutline[i1]) {
                  tmpnr <- as.integer(unlist(strsplit(input[ptr], 
                    split = "="))[2])
                  outlinetmp[[j]] <- matrix(as.numeric(unlist(strsplit(input[(ptr + 
                    1):(ptr + tmpnr)], split = " "))), tmpnr, 
                    2, byrow = TRUE)
                  ptr <- ptr + tmpnr + 1
                  j <- j + 1
                }
                outlineData[[i]] <- outlinetmp
            }
            else outlineData[[i]] <- NA
        }
        names(outlineData) <- nID
        out$outlines <- outlineData
    }
    cat(paste("Read", nobs, "datasets with", sum(noutline), "outlines\n"))
    return(out)
}

>>>>

```
Overall, BL and ML have stronger influence than the other attributes and are related to each other but not with the other attributes throughout time. From the phase 2 to the phase 3, the proportion of TL and SL gets bigger and they are more related to SW.

@@

```
In this plot, we can see that the pattern of correlation for SYG6 and SYG1_1 are similar in terms of correlation based on ML/SL/TL with other attributes. Both are part of the phase 2. However, SYG1_2 is younger than the other two and the correlation based on SW become weaker. 
When it comes to the difference between SYG6 and SYG1_1, the correlation between artifacts of SYG1_1 is stronger than SYG6.

PCA for each site
```{r}
cv_SYG6 + cv_SYG1_1 + cv_SYG1_2 +  plot_layout(ncol=1)
```
Unlike the correlation of the three units, PCA of the three are more various. Especially, SW is related to SL/TL in SYG6, related to ML/BL in SYG1_1, and unrelated to the other attributes in SYG1_2.

```{r}
#I'm working on how to read oulines and how to use them for anlaysis. We may not use this for the research.
# reading landmarks and outline in tps, code from Morpho package, adjust readallTPS function. 
readalltps = function(file) 
{
    out = list()
    exOut <- FALSE
    noutline <- 0
    input <- readLines(file)
    LM <- grep("LM=", input)
    LMstring <- input[LM]
    nLM <- sapply(LMstring, strsplit, split = "=")
    nLM <- unlist(nLM)
    nLM <- as.integer(nLM[-which(nLM == "LM")])
    nobs <- length(nLM)
    ID <- grep("ID=", input)
    IDstring <- input[ID]
    nID <- sapply(IDstring, function(x) {
        x <- gsub("=", "_", x)
    })
    nID <- gsub(" ", "", unlist(nID))
    out$ID <- nID
    outline <- grep("CURVES=", input)
    if (length(outline) > 0) {
        exOut <- TRUE
        outlinestring <- input[outline]
        noutline <- sapply(outlinestring, strsplit, split = "=")
        noutline <- unlist(noutline)
        noutline <- as.integer(noutline[-which(noutline == "CURVES")])
        LMoutline <- (sapply(outline, function(x) {
            x <- max(which(LM < x))
        }))
    }
    LMdata <- list()
    for (i in 1:nobs) {
        if (nLM[i] > 0) {
            LMdata[[i]] <- as.numeric(unlist(strsplit(unlist(input[c((LM[i] + 
                1):(LM[i] + nLM[i]))]), split = " ")))
            LMdata[[i]] <- matrix(LMdata[[i]], nLM[i], 2, byrow = TRUE)
        }
        else LMdata[[i]] <- NA
    }
    names(LMdata) <- nID
    out$LM <- LMdata
    if (exOut) {
        outlineData <- list()
        for (i in 1:nobs) {
            if (i %in% LMoutline) {
                i1 <- grep(i, LMoutline)
                outlinetmp <- list()
                ptr <- outline[i1] + 1
                j <- 1
                while (j <= noutline[i1]) {
                  tmpnr <- as.integer(unlist(strsplit(input[ptr], 
                    split = "="))[2])
                  outlinetmp[[j]] <- matrix(as.numeric(unlist(strsplit(input[(ptr + 
                    1):(ptr + tmpnr)], split = " "))), tmpnr, 
                    2, byrow = TRUE)
                  ptr <- ptr + tmpnr + 1
                  j <- j + 1
                }
                outlineData[[i]] <- outlinetmp
            }
            else outlineData[[i]] <- NA
        }
        names(outlineData) <- nID
        out$outlines <- outlineData
    }
    cat(paste("Read", nobs, "datasets with", sum(noutline), "outlines\n"))
    return(out)
}
